The effects of priming in human computation

### 2014-05-07 docs/draft/pnas1.tex
finish reworking intro (pnas manuscript)

Such platforms human cognition as fluid a resource as compute cycles: it is 
available on demand in small units, with low transaction cost, from anywhere 
via the Internet \footnote{\href{http://mturk.com}{http://mturk.com}}.  The 
result is that one can treat AMT like a compute cluster, and seemlessly 
integrate human and machine intelligence in large-scale computations.

This development invites a new perspective on the role of human cognition 
itself in technical systems.  Researchers have put forward the term HPU 
(Human co-Processing Unit)\footnote{We acknowledge the irony of this term:
the original meaning of `computer' was a person who performs computations,
its reference to machines being a personification brought into usage some time
after 1900}, viewing the introduction of 
microtask represents a fundamentally new computing architecture, in the same
way that the GPUs differ from CPUs \cite{5543192}.  Thinking of networked 
people as computate systems is not new.  Working in operations research, Simon 
and Newell held the primary activity of human organizations to be 
computation\cite{Simon:1958fp}.

@@

We test hysteresis by presenting AMT workers with
five images that depict meals with strong cultural overtones, and ask them to
label each image with descriptive words.  Before presenting test images,
we expose the workers to different priming treatments.  We observe how priming
treatments effect the workers' subsequent choice of labels, by looking at 
how specific the labels are in their meaning, and how often workers make 
cultural references.

We employ two priming modalities in this study.  
In the first modality, which we call \textit{in-task priming}, workers are 
shown one of three sets of priming images.  The \textit{cultural}
image set, \textbf{Fig. 2}, shows images chosen for their clear depiction of a 
iconic cultural scene.  The \textit{ingredients} image set, \textbf{Fig. 3}, 
shows separated food ingredients, as opposed to the prepared meals shown in 
the test set, and avoids strong cultural signal.  The \textit{ambiguous} 
image set contains images of prepared meals, similar to the test set, but 
traces of cultural references are not prominent.  These images are shown right
before the test images, and they must be labeled in the same way.  From the 
workers' view-point there is no distinction between the priming and test 
images.

@@

The measurement of priming effects, however, traditionally involves a prior
assumption of what those effects will be.  At risk of circularity, but lacking
alternatives, the definition of priming itself traditionally becomes 
operationalized in terms of these effects\cite{}.  We seek to alleviate this 
situation by providing an application-independant definition of priming 
suitable for use in studying the computational properties of HPUs.

In the remainder of the introduction, we review prior work in human 
computation and priming.  In the next section, \textbf{Analytical Framework},
we introduce our definition of priming, before presenting our experimental 
\textbf{Results}, \textbf{Discussion}, and \textbf{Conclusion}.  
We present our \textbf{Methods} in detail at the end of the paper.

>>>>

Such platforms render human cognition as fluid a resource as compute cycles: 
it is available on demand in small units, with low transaction cost, from 
anywhere 
via the Internet \footnote{\href{http://mturk.com}{http://mturk.com}}.  The 
result is that one can treat AMT like a compute cluster, and seemlessly 
integrate human and machine intelligence in large-scale computations.

This development invites a new perspective on the role of human cognition 
in technical systems.  Researchers have put forward the term HPU 
(Human co-Processing Unit)\footnote{We acknowledge the irony of this term:
the original meaning of `computer' was a person who performs computations,
its reference to machines being a personification brought into usage in the 
late 1800s\cite{Dictionary:hl}.}, viewing the introduction of 
microtask platforms as a fundamentally new computing architecture
\cite{5543192}.  Thinking of networked 
people as compute systems is not new.  Working in operations research, Simon 
and Newell viewed the primary activity of human organizations to be 
computation\cite{Simon:1958fp}.

@@

We test hysteresis by presenting AMT workers with
five images that depict meals with strong cultural overtones, and ask them to
label each image with descriptive words.  Before presenting test images,
we expose the workers to different priming treatments.  We observe how priming
treatments effect the workers' subsequent choice of labels, by looking at 
how specific the labels are, and how often workers make 
cultural references.

We employ two priming modalities in this study.  
In the first modality, which we call \textit{in-task priming}, workers are 
shown one of three sets of priming images.  The \textit{cultural}
image set, \textbf{Fig. 2}, shows images chosen for their clear depiction of an
iconic cultural scene.  The \textit{ingredients} image set, \textbf{Fig. 3}, 
shows separated food ingredients, as opposed to the prepared meals shown in 
the test set, and avoids strong cultural signal.  The \textit{ambiguous} 
image set contains images of prepared meals, and is most similar to the test 
set, but there are no prominent traces of cultural reference.  These images 
are shown right
before the test images, and they must be labeled in the same way.  From the 
workers' view-point there is no distinction between the priming and test 
images.

@@

However, to measure the effects of priming, one generally has to make an 
assumption about what those effects will be.  At risk of circularity, the 
definition of priming itself is traditionally operationalized in terms 
of these effects \cite{}.  We seek to alleviate this 
situation by providing an application-independant definition of priming 
suitable for studying HPUs hysteresis.  We 
present this definition following the section on prior work.
